### 2024-02-28 Scripts/Manuscript/manuscript.Rmd
added endpoint_check, failed to add replicate check.
changed plot456 and plot46, and first stages of restructuring results.

classoption       : "man"
output            : papaja::apa6_pdf
knit              : worcs::cite_all
---

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(tidyr)
library(betareg)
library(lmerTest)
library(psych)
library(forcats)
library(GPArotation)
library(ggplot2)
library(ggridges)
library(GGally)
library(ggforce)
library(grid)
library(gridExtra)

# loading source script
source(file = "../source_script.R")

@@

Several explanations for this discrepancy between original and replication findings have been suggested and investigated, with many being centred around the concept of Questionable Research Practices [QRPs, @john2012measuring]. QRPs are practices, which either misrepresent or omit essential methodological information that is necessary for the evaluation of the research. Without this information, a reader will not know whether the result was in line with the author's expectation or simply the result of repeated trial and error until a suitable result was found [@simmons2011false]. Consequently, much of the discourse and the subsequent proposed solutions have been centred around preventing these QRPs through increased transparency in scientific reporting. Preregistrations are one method for preventing QRPs. Preregistrations provide a clear description of the originally planned methodology of a study, which remains publicly available alongside the final report of the study. As a result, the author's original expectations and intentions can be accessed by the reader [@nosek2022replicability].

@@

Measurement in psychological science is defined in large part by one overarching issue: psychological constructs, such as affective state and intelligence, cannot be measured directly. As a result, psychologists face two primary challenges in the use of measurement: First of all, the measure has to assess the construct it intends to measure, even though it can only do so indirectly. Secondly, because the measurement is indirect, it also comes with some degree of error surrounding its assessment of the construct. The first issue relates to the concept of validity, and specifically construct validity. Validity refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity specifically refers to the substantial relation between the item scores on a psychological measure and the psychological construct it intends to measure. In order for indirect assessment of psychological constructs to be a viable approach, the measure needs to have construct validity [@cook2002experimental]. However, both original and replication research are often not reported with sufficient details on construct validity [@shaw2020measurement; @flake2022construct]. The second issue relates to the concept of measurement error and reliability. Measurement error indicates the amount of variation in item scores that is the result of the used measures inaccuracies, and not due to differences in the underlying psychological construct of interest. While what should be considered acceptable levels of measurement error is a subject of debate, and dependent upon context [@cho2015cronbach], it is generally agreed upon that too much measurement error is problematic. If measurement error is too large, the item scores relate to a construct no more than they do to random noise. As a result, the interpretability of these scores as indicators of a psychological construct is limited.

@stanley2014expectations demonstrated, using a simulation study, the drastic effect measurement error can have on attempts to verify or falsify original findings. In practice, measurement error is commonly indicated using score-reliability. Score-reliability is an index of consistency of a measure, showing how much the items converge to the same point, with the point being the measured variable. Thus, @stanley2014expectations generated scalar item data with levels of score-reliability that mimicked what is standard in psychological research, to ensure that the resulting degree of measurement error was representative. Using this data, they found that the degree of measurement error can explain a large amount of the variation in observed effects found in replication research. It could therefore be that a failed replication was simply the result of measurement of the true effect varying from the original, rather than the true effect itself being different from what was originally reported. As a result, interpretations of replications might not be based on tests of the true effect, if the impact of measurement error is not attenuated for.

Another key aspect in evaluating the use of measures is how they are reported. Questionable Measurement Practices (QMPs) have been coined as a conjugate term to QRPs. QMPs are practices that decrease the information necessary to evaluate the measurement of a study. They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement]. @flake2022construct coded the presence of a series of QMPs in the replication report in both the replication protocols of each replication in the RPP, as well as the original articles the replications were based on. They found that QMPs linked to issues for replicators in recreating the measurement to closely match the measurement in the original. As a result, there was a lack of measurement related information in both replication reports, and original articles. Without this information, it becomes difficult to establish that original and replication are measuring the same construct(s), which has detrimental consequences for direct replication attempts.

@@

As a first step it is worth investigating what the state of measurement error is in original and psychological research, in order to assess the scope of @stanley2014expectations's findings in practice. Thus, this study investigated the following:

@@

It is difficult to suggest an expected or informed cut-off value for what could be considered a sufficient score reliability coefficient for both original and replication studies. While suggested cut-off points for reliability do exist [@nunnaly1994assessment], they are not without their criticism [@cho2015cronbach; @crutzen2017scale]. Instead a comparison of scores between original and their associated replication studies should be of more substantive interest. Since direct replications intend to investigate effects in nearly identical scenarios with nearly identical measures as the original study, it is expected that measurement errors are as present in replication research as in original psychological research.

@@

While reliability estimates are generally considered a measure specific feature, this is false. They are context dependent, and as a result the estimates of an effect can differ across contexts [@cho2015cronbach; @pauly2018resampling]. With large enough differences across contexts, the effect estimates between different replication attempts could deviate from each other beyond direct comparison. For instance, suppose that we have a measure of multiple items assessing agreeableness in relation to both parents as well as peers. In a non-traditional society we might find high reliability for this measure, because participants that score high on one item, score high on another item since they are generally agreeable, while participants that score low one item, score low for all the other items. On the other hand, in a more traditional society we might find that reliability is low, because agreeableness towards parents is normative in that society, and as a result items relating to agreeableness towards parents may not be indicative of general agreeableness as a personality trait. In this example, a high score on the measure in the first context relates more strongly to a single agreeableness construct compared to the second context. The findings across these two populations would then no longer be directly comparable. Consequently, the value of any direct replication would become limited. To investigate this potential problem, the variation in score reliability is assessed for each measure when used in different contexts.

@@

Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates. An example of the standardising impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved]. Heterogeneity refers to the true variation in the true effect size due to minor but key differences in context, environment, and procedure. Heterogeneity is yet another proposed explanation for failed replications. This concern even prompted a Many Labs centred around the testing of heterogeneity in replications [@klein2018many]. However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects amongst replications. These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.

@@

Reliability is only one aspect by which a measure can be judged, with validity being another important way to determine the scientific rigour of a measure [@roberts2006reliability]. Therefore as part of the exploratory analyses, validity was assessed for the same data source used to test the aforementioned hypotheses. Specifically, the unidimensionality of the measure was determined, meaning whether or not the items of a measure all related to a single variable.

@@

@flake2022construct descriptively investigated QMPs within the reproducibility project psychology [@osc2015estimating]. This study seeks to conceptually replicate some of their findings within the Many Labs replication projects.

@@

The investigations by @flake2022construct have shown not only that QMPs are common in psychological research, they can be even more common in replications reports. However, the reporting of the Many Labs projects differ from the RPP data used in @flake2022construct. The structured and preregistered protocols used for the Many Labs projects were hypothesized to lead to consistent reporting of important measurement details, and as a result contain less QMPs.

@@

QMPs put the validity of a study into question. If there is a lack of transparency and the used measures are invalid, replication results become difficult to interpret [@flake2020measurement]. With a lack of transparency, closely mimicking the original's measurement becomes challenging. Furthermore, if a replication does not properly measure the variables of the original effect, the effect analysed within the replication may not be the same as the original. For these reasons, establishing a link between QMPs and non-replicability should confirm suspicions of their detrimental effects on replications [@flake2017construct; @flake2020measurement; @flake2022construct].

@@

@flake2022construct have already demonstrated the issues replicators face in transparently reporting the appropriate evidence for the measures they used. That study identified among other issues, a lack of available information in original articles. If essential information on a measure is not available in an original article, it may be difficult to know the specifics of that measure when used in a replication. In that case, the lack of proper reporting on measurement would impact the transparency and validity of future replications. Consequently, the article's findings become difficult to verify. To provide insight into this issue, an investigation of the relationship between original and replication QMPs was included.

@@

If the relationship exists, it is expected that questionable measurement practices in an original paper might cause a spill-over effect of QMPs into the replication. If the original paper does not specify how a measure was used, the replication may implement it differently. In that case, the replication can no longer be considered a direct replication. Additionally, investigations by @shaw2020measurement have shown that more validity evidence in an original article is associated with better psychometric properties in the replication sample. Based on these arguments, hypotheses are expected to be associated across original and replication studies.

@@

The data used for the analyses in this study consists of three main sources: replication datasets, preregistered replication protocols, and original study articles. The data came from the Many Labs series of studies. In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many]. Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs. Additionally, the replication of [@crosby2008we] in Many Labs 5 did not contain contain data suitable for this project. The replication made use of videos and eye-tracking as measures, which does not match this study's focus on scale and item measures.

The total number of psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of 60: 13 in Many Labs 1; 28 in Many Labs 2; 10 in Many Labs 3; & finally 9 out of the 10 tested findings in Many Labs 5. Since each replication set is related to an original study, the number of effects in original studies matches the number of effects in replication research.

However, the unit of measurement was not a single study or replication. Instead each measure of a unique variable within a Many Labs project was treated as the unit of measurement. The reason being that studies could have and did use multiple measures. Additionally, measures can assess multiple dimensions. These dimensions, meaning unique variables, were separated into different units whenever possible, otherwise the measure was discarded from analysis. However, not all measures of unique variables were used. Only data from measures of primary variables, meaning those variables included in the primary test of the replication, were used. This was done to ensure that the analyses could link directly to the replicability of a study. Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included. The result was a total sample size of 77 measures: 14 in Many Labs 1; 35 in Many Labs 2; 15 in Many Labs 3; & 13 in Many Labs 5. Again, the sample was equivalent between replications and original studies.

@@

The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study. The specific data was extracted from the replication datasets for each relevant measure. The measure had to consist of multiple scalar items to be considered relevant for the related analyses. Single item measures were not usable for the analyses on score reliability [@wanous1996estimating] as they do not translate directly to the findings of @stanley2014expectations, which this study is following up on.

For Many Labs 1, all the relevant replication data was available in a single csv file. For Many Labs 2 & 3 the situation was similar, only here the files were split across two csv files for each project. For Many Labs 5, the data was made available for each of the ten replication sets separately. Three out of the ten datasets were furthermore split across the various locations at which they were taken. If cleaned data was available this was chosen over raw data. Pilot data were omitted from the analyses entirely. This resulted in suitable measure data from eighteen replication sets spread across on average 40 lab locations for the analyses of hypotheses 2 & 3.

@@

### ML 2
# 2.2
data_2.2_clean <- cbind(as.factor(data_2.2[[5]]), data_2.2[6:11])
colnames(data_2.2_clean)[1] <- "g"
# 2.3
# data does not appear suitable
# 2.4.1
data_2.4.1_clean <- cbind(as.factor(data_2.4.1[[5]]), data_2.4.1[6:11])
colnames(data_2.4.1_clean)[1] <- "g"
# 2.4.2
data_2.4.2_clean <- cbind(as.factor(data_2.4.2[[5]]), data_2.4.2[6:14])
colnames(data_2.4.2_clean)[1] <- "g"
# 2.8.2
data_2.8.2_clean <- cbind(as.factor(data_2.8.2[[6]]), data_2.8.2[9:13])
colnames(data_2.8.2_clean)[1] <- "g"
# 2.10.1
data_2.10.1_clean <- cbind(as.factor(data_2.10.1[[5]]), data_2.10.1[6:11])
colnames(data_2.10.1_clean)[1] <- "g"
# 2.12.1
data_2.12.1_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(6,7,8,9,10,31,32,33,34,35)]) 
data_2.12.1_clean[3465:6905,2:6] <- data_2.12.1_clean[3465:6905,7:11]
data_2.12.1_clean <- data_2.12.1_clean[1:6]
colnames(data_2.12.1_clean)[1] <- "g"
# 2.12.2
data_2.12.2_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(11,14,15,18,19,22,24,27,28,29,36,39,40,43,44,47,49,52,53,54)]) 
data_2.12.2_clean[3465:6905,2:11] <- data_2.12.2_clean[3465:6905,12:21]
data_2.12.2_clean <- data_2.12.2_clean[1:11]
colnames(data_2.12.2_clean)[1] <- "g"
# 2.12.3
data_2.12.3_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(12,13,16,17,20,21,23,25,26,30,37,38,41,42,45,46,48,50,51,55)]) 
data_2.12.3_clean[3465:6905,2:11] <- data_2.12.3_clean[3465:6905,12:21]
data_2.12.3_clean <- data_2.12.3_clean[1:11]
colnames(data_2.12.3_clean)[1] <- "g"
# 2.15
data_2.15_clean <- cbind(as.factor(data_2.15[[5]]), data_2.15[8:12])
colnames(data_2.15_clean)[1] <- "g"
# 2.19.1
# difficult to extract
# 2.19.2
# difficult to extract
# 2.20
data_2.20_clean <- cbind(as.factor(data_2.20[[5]]), data_2.20[6:45] - 1) 
data_2.20_clean[3729:7396,2:21] <- data_2.20_clean[3729:7396,22:41]
data_2.20_clean <- data_2.20_clean[1:21] 
colnames(data_2.20_clean)[1] <- "g"
# 2.23
data_2.23_clean <- cbind(as.factor(data_2.23[[5]]), data_2.23[c(7,8,12,13,15)])
colnames(data_2.23_clean)[1] <- "g"

@@

### ML 5
# 5.1.1
data_5.1.1_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[13:33])
colnames(data_5.1.1_clean)[1] <- "g"
# 5.1.2
# difficult to separate .1 from .2
# 5.4
data_5.4_clean <- cbind(as.factor(data_5.4[[1]]), data_5.4[18:41])
colnames(data_5.4_clean)[1] <- "g"
# 5.5.1 & 5.5.2
# from this dataset it appears that this data will be difficult to use.
# 5.5.2
# also difficult to use
# 5.7 
data_5.7_clean <- cbind(as.factor(data_5.7[[3]]), data_5.7[c(25, 34, 35, 36, 37, 38, 39, 40, 41, 42)])
colnames(data_5.7_clean)[1] <- "g"
# 5.9.1
data_5.9.1_clean <- na.omit(cbind(as.factor(data_5.9.1[[4]]), data_5.9.1[c(79, 83, 87, 91, 95, 98, 101)]))
colnames(data_5.9.1_clean)[1] <- "g"

@@

@@

The preregistered replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each replication set. These protocols were available through the OSF pages of each Many Labs project. These preregistered replication protocols, as well as the replication datasets mentioned earlier were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. This includes any systematic coding of the QMPs present in the report. Furthermore, no overview of these and the qualitative topics were available at the time of preregistration.

@@

The original study articles are the published articles of the original effect on which the Many Labs replication sets were based. In the case of Many Labs 5 the original studies refer to the studies which first tested the effect to be replicated, not the earlier replication attempts of the same effects in the RPP [@osc2015estimating].

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. When available, codebooks and study materials were used to identify the specific data for each measure.

The publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base] Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each measure were extracted into their own data frame containing the data from all studies in one replication set. These pieces of information formed the replication datasets in the analysis.

The OSF page for each Many Labs project was combed through, in order to identify the components of the research which contained information on the measurement practice and reported reliability. The focus was on finding the preregistered protocols which contained information on the entirety of the replication sets in each Many Labs project. This was successful for Many Labs 2, & 3. For Many Labs 1 the Proposal_V1.1 was selected as the proper candidate for the QMP analysis. Despite the difference in name, it is the equivalent in Many Labs 1 to the protocols of Many Labs 2 & 3. For Many Labs 5 the protocols were made accessible for each replication set separately. The relevant OSF page of each replication set was searched through for a file which contained protocol in its name. If available, a version of the protocol labelled as revised, post-review, peer-review, or endorsed was selected. In case there was doubt about which was most appropriate, the latest uploaded relevant protocol was selected. Only regular protocols were taken, meaning those not labelled as data collection, analysis protocol or anything similar[^1].

The original articles were identified through the citations in each replication protocol, using Web of Science, Google Scholar, and PsychInfo (in that order). An issue was encountered while trying to access @hyman1950current. However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained for use in the analyses.

The measures of primary variables were identified by combing through the entire methods section of each preregistered replication protocols. Then using the structured coding protocol (made using Qualtrics) that is available on the OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages of this study, each measure of a unique variable was coded on measurement reporting and reported reliability.

>>>>

classoption       : "man"
output            : papaja::apa6_pdf
knit              : worcs::cite_all
bibliography: references.bib
---

```{r setup, include = FALSE}
# loading R libraries
library(papaja)
library(worcs)
library(tidyr)
library(betareg)
library(lmerTest)
library(psych)
library(forcats)
library(GPArotation)
library(ggplot2)
library(ggridges)
library(GGally)
library(ggforce)
library(grid)
library(gridExtra)
library(metafor)

# loading source script
source(file = "C:/Users/u686785/OneDrive - Tilburg University/Documents/uvt/PHD/Master Thesis to Paper/Reproducible_R_Project/Scripts/source_script.R")

@@

Several explanations for this discrepancy between original and replication findings have been suggested and investigated, with many being centred around the concept of Questionable Research Practices [QRPs, @john2012measuring]. QRPs are practices, which either misrepresent or omit essential methodological information that is necessary for the evaluation of the research. Without this information, a reader will not know whether the result was in line with the author's expectation or simply the result of repeated trial and error until a suitable result was found [@simmons2011false]. Consequently, much of the discourse and the subsequent proposed solutions have been centred around preventing these QRPs through increased transparency in scientific reporting.

@@

Measurement in psychological science is defined in large part by one overarching issue: psychological constructs, such as affective state and intelligence, cannot be measured directly. As a result, psychologists face two primary challenges in the use of measurement: First of all, the measure has to assess the construct it intends to measure, even though it can only do so indirectly. Secondly, because the measurement is indirect, it also comes with some degree of error surrounding its assessment of the construct. The first issue relates to the concept of validity, and specifically construct validity. Validity refers to the overall extent to which a measure measures what it is supposed to [@borsboom2004concept], while construct validity specifically refers to the substantial relation between the item scores on a psychological measure and the psychological construct it intends to measure. In order for indirect assessment of psychological constructs to be a viable approach, the measure needs to have construct validity [@cook2002experimental]. The second issue relates to the concept of measurement error and reliability. Measurement error indicates the amount of variation in item scores that is the result of the used measures inaccuracies, and not due to differences in the underlying psychological construct of interest.

@stanley2014expectations demonstrated, using a simulation study, the impact measurement error has on attempts to verify or falsify findings. Scalar item data was generated based on levels of sampling error and score-reliability, as the inverse of measurement error, that mimicked what is standard in psychological research, to ensure that the resulting degree of error was representative. The results indicated that measurement error caused observed effects found in replication research to vary heavily. ???relation measurement error and replicability (As a result, interpretations of replications might not be based on tests of the true effect, if the impact of measurement error is not attenuated for.)???

Another key aspect in evaluating the use of measures is how they are reported. Questionable Measurement Practices (QMPs) have been coined as a conjugate term to QRPs. QMPs are practices that decrease the information necessary to evaluate the measurement of a study. They range from lack of transparency and unclear motivation in choice of measure, to poor justification for modifications of measure and procedure of any sourced measures [@flake2020measurement]. When this information is missing, it becomes difficult to establish that original and replication are measuring the same construct(s), which has detrimental consequences for direct replication attempts.

@@

???connection/throughline of the measurement error hypotheses and other (including measurement error) hypotheses –\> is there a way to rewrite this part of the article to fit better as support/precedence to the QMP stuff???? –\> risky use of measurement!?!

As a first step it is worth investigating what the state of measurement error is in original and replication research in psychology, in order to assess the scope of @stanley2014expectations's findings in practice. Thus, this study investigated the following:

@@

Since direct replications intend to investigate effects in nearly identical scenarios with nearly identical measures as the original study, it is expected that measurement errors are as present in replication research as in original psychological research.

@@

While reliability estimates are generally considered a measure specific feature, this is false. They are context dependent, and as a result the estimates of an effect can differ across contexts [@cho2015cronbach; @pauly2018resampling]. With large enough differences across contexts, the effect estimates between different replication attempts could deviate from each other beyond direct comparison. ???RELIABILITY VARIANCE IN META ANALYSIS???. To investigate this potential problem, the variation in score reliability is assessed for each measure when used in different contexts.

@@

Even though reliability estimates are context dependent, sufficient protocol structure can counteract the variance in reliability estimates. An example of the standardising impact a structured protocol can have on reducing variability within an effect can be found in investigations into the closely related issue of heterogeneity [@patacchini2007unobserved]. Heterogeneity refers to the true variation in the true effect size due to minor but key differences in context, environment, and procedure. Heterogeneity is yet another proposed explanation for failed replications. This concern even prompted a Many Labs centred around the testing of heterogeneity in replications [@klein2018many]. However analyses from Many Labs 2, and @olsson2020heterogeneity showed little empirical evidence for widespread heterogeneity in effects among replications. These findings demonstrate that it is possible to reduce variability as the result of context using structured protocols, as was done in the Many Labs projects this study analyzed.

@@

@@

This study seeks to conceptually replicate some of the findings of @flake2022construct about QMP reporting in the RPP within the Many Labs replication projects.

@@

@flake2022construct coded the presence of a series of QMPs in the replication report in both the replication protocols of each replication in the RPP, as well as the original articles the replications were based on. They found that not only are QMPs common in psychological research, they can be even more common in replications reports. However, the reporting of the Many Labs projects differ from the RPP data used in @flake2022construct. The structured and preregistered protocols used for the Many Labs projects were hypothesized to lead to consistent reporting of important measurement details, and as a result contain less QMPs.

@@

QMPs may obscure relevant information needed to evaluate the use of measurement in a study. If the replication used the measure differently from the original, the replication may no longer be a direct replication. ???link not direct replication to lack of replication through larger variance argument??? For these reasons, establishing a link between QMPs and non-replicability should confirm suspicions of their detrimental effects on replications [@flake2017construct; @flake2020measurement; @flake2022construct].

@@

This study additionally aims to see if the relation between QMPs and replicability can be traced back to original article QMPs. When essential information on a measure is not available in an original article, it may be difficult to know the specifics of that measure to report for a replication. Therefore this study also investigates the relation between original QMPs and replication QMPs.

@@

If the relationship exists, it is expected that questionable measurement practices in an original paper might cause a spill-over effect of QMPs into the replication. @flake2022construct found that QMPs linked to issues for replicators in recreating the measurement to closely match the measurement in the original. As a result, there was a lack of measurement related information in both replication reports, and original articles. Additionally, investigations by @shaw2020measurement have shown that more validity evidence in an original article is associated with better psychometric properties in the replication sample. Based on these arguments, QMPs are expected to be associated across original and replication studies.

@@

The data used for the analyses in this study consists of three main sources: replication datasets, preregistered replication protocols, and original study articles. The data came from the Many Labs series of studies. In particular, data from Many Labs 1, 2, 3, & 5 was used [@klein2014investigating; @klein2018many; @ebersole2016many; @ebersole2020many]. Data from Many Labs 4 [@klein2022many] was not part of the sample, as there was no publicly available protocol which contains the information needed to code QMPs. Additionally, the replication of [@crosby2008we] in Many Labs 5 made use of videos and eye-tracking as measures, which did not match this study's focus on scale and item measures.

The total number of psychological findings for which replication was attempted across the four included Many Labs projects amounts to a total of 60. Each finding was tested across several labs, and was related to a finding from an original study, the combination of all these studies and their associated information formed a replication set. For each research finding, any primary measures assessing a unique variable were taken to form the final unit of measurement. Here primary measures refers to measures assessing variables included in the primary test of the replication, were used. This was done to ensure that the analyses could link directly to the replicability of a study. Acquiescence bias checks, manipulation checks, measures used for pilot testing, and measures added for exploratory analyses in replication studies were not included.. The result was a total sample size of 77 measures. The Table BELOW show descriptive information about the data for each Many Labs Project.

DESCRIPTIVE TABLE

(Row 1: Many Labs projects - 13 in Many Labs 1; 28 in Many Labs 2; 10 in Many Labs 3; & finally 9 out of the 10 tested findings in Many Labs 5)

(Row 2: Primary measures - 14 in Many Labs 1; 35 in Many Labs 2; 15 in Many Labs 3; & 13 in Many Labs 5)

(Row 3: ???)

Footnote about sample size differences between original and original shortened.

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that the planned analyses were feasible. However, no coding or analysis of either of them had taken place before the analyses were preregistered. When available, codebooks and study materials were used to identify the specific data for each measure.

@@

The replication datasets refer to the data of each of the replication attempts for each of the original psychological effects undertaken as part of a Many Labs study. These publicly available datasets of the replication attempt were accessed through their OSF page and loaded into Rstudio [@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base] Using the replication protocols, codebooks, and analysis scripts from each replication set as a guide, the variables associated with each relevant measure were extracted into their own data frame containing the data from all studies in one replication set. These pieces of information were used as the datasets in the analysis.

The measure had to consist of multiple scalar items to be considered relevant, as single item measures were not usable for the planned analyses on score reliability [@wanous1996estimating], which followed up on @stanley2014expectations simulation study. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended. Pilot data were omitted from the analyses entirely. These criterion resulted in suitable measure data from eighteen replication sets spread across on average 40 lab locations for the analyses of hypotheses 2 & 3.

DESCRIPTIVE TABLE???

@@

### ML 2
# 2.2
data_2.2_clean <- cbind(as.factor(data_2.2[[5]]), data_2.2[6:11])
colnames(data_2.2_clean)[1] <- "g"
# 2.3
# data does not appear suitable
# 2.4.1
data_2.4.1_clean <- cbind(as.factor(data_2.4.1[[5]]), data_2.4.1[6:11])
colnames(data_2.4.1_clean)[1] <- "g"
# 2.4.2
data_2.4.2_clean <- cbind(as.factor(data_2.4.2[[5]]), data_2.4.2[6:14])
colnames(data_2.4.2_clean)[1] <- "g"
# 2.8.2
data_2.8.2_clean <- cbind(as.factor(data_2.8.2[[6]]), data_2.8.2[9:13])
colnames(data_2.8.2_clean)[1] <- "g"
# 2.10.1
data_2.10.1_clean <- cbind(as.factor(data_2.10.1[[5]]), data_2.10.1[6:11])
colnames(data_2.10.1_clean)[1] <- "g"
# 2.12.1
data_2.12.1_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(6,7,8,9,10,31,32,33,34,35)]) 
data_2.12.1_clean[3465:6905,2:6] <- data_2.12.1_clean[3465:6905,7:11]
data_2.12.1_clean <- data_2.12.1_clean[1:6]
colnames(data_2.12.1_clean)[1] <- "g"
# 2.12.2
data_2.12.2_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(11,14,15,18,19,22,24,27,28,29,36,39,40,43,44,47,49,52,53,54)]) 
data_2.12.2_clean[3465:6905,2:11] <- data_2.12.2_clean[3465:6905,12:21]
data_2.12.2_clean <- data_2.12.2_clean[1:11]
colnames(data_2.12.2_clean)[1] <- "g"
# 2.12.3
data_2.12.3_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(12,13,16,17,20,21,23,25,26,30,37,38,41,42,45,46,48,50,51,55)]) 
data_2.12.3_clean[3465:6905,2:11] <- data_2.12.3_clean[3465:6905,12:21]
data_2.12.3_clean <- data_2.12.3_clean[1:11]
colnames(data_2.12.3_clean)[1] <- "g"
# 2.15
data_2.15_clean <- cbind(as.factor(data_2.15[[5]]), data_2.15[8:12])
colnames(data_2.15_clean)[1] <- "g"
# 2.19.1
# difficult to extract
# 2.19.2
# difficult to extract
# 2.20
data_2.20_clean <- cbind(as.factor(data_2.20[[5]]), data_2.20[6:45]) 
data_2.20_clean[3729:7396,2:21] <- data_2.20_clean[3729:7396,22:41]
data_2.20_clean <- data_2.20_clean[1:21] 
# coding so all 1's means somebody used rule-based grouping strategy
data_2.20_clean[,c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20)] <- ifelse(data_2.20_clean[,c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20)] == 1, 1, 0)
data_2.20_clean[,c(3, 5, 7, 9, 11, 13, 15, 17, 19, 21)] <- ifelse(data_2.20_clean[,c(3, 5, 7, 9, 11, 13, 15, 17, 19, 21)] == 2, 1, 0)
colnames(data_2.20_clean)[1] <- "g"
# 2.23
data_2.23_clean <- cbind(as.factor(data_2.23[[5]]), data_2.23[c(7,8,12,13,15)])
colnames(data_2.23_clean)[1] <- "g"

@@

### ML 5
# 5.1.1
data_5.1.1_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[13:27])
colnames(data_5.1.1_clean)[1] <- "g"
# 5.1.2
data_5.1.2_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[28:33])
colnames(data_5.1.2_clean)[1] <- "g"
# 5.4
data_5.4_clean <- cbind(as.factor(data_5.4[[1]]), data_5.4[18:41])
colnames(data_5.4_clean)[1] <- "g"
# 5.5.1 & 5.5.2
# from this dataset it appears that this data will be difficult to use.
# 5.5.2
# also difficult to use
# 5.7 
data_5.7_clean <- cbind(as.factor(data_5.7[[3]]), data_5.7[c(25, 34, 35, 36, 37, 38, 39, 40, 41, 42)])
colnames(data_5.7_clean)[1] <- "g"
# 5.9.1
data_5.9.1_clean <- na.omit(cbind(as.factor(data_5.9.1[[4]]), data_5.9.1[c(79, 83, 87, 91, 95, 98, 101)]))
colnames(data_5.9.1_clean)[1] <- "g"

@@

open_data(data = data_5.1.2_clean, filename = paste0(paste0(
  "Data/IntermediateData/", deparse(substitute(data_5.1.2_clean))), ".csv"),
  codebook = paste0(paste0(
    "Data/IntermediateData/codebook_", 
    deparse(substitute(data_5.1.2_clean))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/IntermediateData/value_labels_", 
    deparse(substitute(data_5.1.2_clean))), ".yml"))

@@

The preregistered replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each replication set. These protocols were available through the OSF pages of each Many Labs project.

The OSF page for each Many Labs project was combed through, in order to identify the components of the research which contained information on the measurement practice and reported reliability. The focus was on finding the preregistered protocols which contained information on the entirety of the replication sets in each Many Labs project. For Many Labs 2, & 3 a common protocol could be identified, for Many Labs 1 the Proposal_V1.1 provided the equivalent information, while for Many Labs 5 protocols were available for each replication set separately.

MAKE ALL FOOTNOTE?: (in reference to ML 5 mostly) The relevant OSF page of each replication set was searched through for a file which contained protocol in its name. If available, a version of the protocol labelled as revised, post-review, peer-review, or endorsed was selected. In case there was doubt about which was most appropriate, the latest uploaded relevant protocol was selected. Only regular protocols were taken, meaning those not labelled as data collection, analysis protocol or anything similar[^1].

@@

The original study articles are the published articles of the original effect on which the Many Labs replication sets were based. In the case of Many Labs 5 [@ebersole2020] the original studies refer to the studies which first tested the effect to be replicated, not the earlier replication attempts of the same effects in the RPP [@osc2015estimating].

FOOTNOTE:The original articles were identified through the citations in each replication protocol, using Web of Science, Google Scholar, and PsychInfo (in that order). An issue was encountered while trying to access @hyman1950current. However, after contacting the first author of @klein2014investigating a suitable version of the article was obtained for use in the analyses.

@@

The measures of primary variables were identified by combing through the entire methods section of each preregistered replication protocols. Then using questions and the accompanying search strategies as documented in the structured coding protocol of this study (available on the relevant OSF: <https://osf.io/9r8yt/>, and github pages: <https://github.com/CasGoos/measurement_and_replication.git>), information on the reported measurement evidence and reporting quality was assessed for both replication protocols and original studies. Descriptions of the extracted variables can be found in the [Measures](#Measures) section below. Exact descriptions of the search strategy can be found in Appendix ???.

MOVE TO APPENDIX/COMBINE WITH EXTERNAL SEARCH STRATEGY FILE: The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections. Additionally, a keyword search using the name of the measured variable was used to search for any potentially missed information. An exception to this procedure was a question asking about the presence of example items. For this question, information from supplementary materials was uniquely considered as relevant. Another exception was the question regarding the replication of the original effect. Tables from the final report of each Many Labs project were used to answer that question.

After the data was initially coded according to the preregistered coding protocol, it was determined, based on discussion with the supervisor, that some of the initial ratings were possibly to stringent. As a result, some of the items in the protocol were reformulated, so that the conclusions from the resulting analyses were based on a more lenient judgement of QMPs. The revision of the coding protocol happened after all the data were coded using the initial protocol. As a result the coded data using the initial protocol, and the coded data using the revised protocol are both available available on this article's OSF (<https://osf.io/9r8yt/>) and github (<https://github.com/CasGoos/measurement_and_replication.git>) pages.

MOVE TO APPENDIX/COMBINE WITH EXTERNAL SEARCH STRATEGY FILE: These changes included: accepting linked online appendices as a data source for example items; assuming that if no differences between replication and original are measurement is mentioned, that there is no difference, even if it is not explicitly clear; and generally simplified criteria for what constituted sufficiently clear reporting.
